#Code to run the optimisation side of the analysis
```{r "knitr config", cache = FALSE, include=FALSE}
require("knitr")
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```
#Import packages
```{r}
# remotes::install_github("prioritizr/prioritizr@fix-problem-dgcmatrix")
# load packages
library(prioritizr)
library(remotes)
library(lifecycle)
library(usethis)
library(devtools)
library(prioritizrdata)
library(sf)
library(raster)
library(terra)
library(gurobi)
library(Matrix)
library(parallel)
library(data.table)
rm(list=ls())

# Get the number of CPU cores
num_cores <- detectCores()
cat("Number of CPU cores:", num_cores, "\n")
options(scipen = 999)
getwd()
```
#Set up folders
```{r}
v <- "v5"
# Create output folders 
outfolder <- paste0("./outputs_", v)
outfoldermaps <- paste0("./outputs_", v, "/maps_", v)
outfoldervals <- paste0("./outputs_", v, "/vals_", v)
outfolderrasts <- paste0("./outputs_", v, "/rasters_", v)
outfolderresults <- paste0("./outputs_", v, "/results_", v)

# Create folders:
if (!dir.exists(outfoldermaps)){
  dir.create(outfoldermaps, recursive = TRUE)
} else {
  print("Dir already exists!")
}
if (!dir.exists(outfoldervals)){
  dir.create(outfoldervals, recursive = TRUE)
} else {
  print("Dir already exists!")
}
if (!dir.exists(outfolderrasts)){
  dir.create(outfolderrasts, recursive = TRUE)
} else {
  print("Dir already exists!")
}
if (!dir.exists(outfolderresults)){
  dir.create(outfolderresults, recursive = TRUE)
} else {
  print("Dir already exists!")
}

```
#Planning units
```{r}
# Planning units ID layer
sr_ras = raster("inputs/CBD-corrected_countries-code.tif")
base_ras = sr_ras - sr_ras
terrestrial_index = which(!is.na(base_ras[]))
base_ras[terrestrial_index] = 1
plot(base_ras)
pu_val <- values(base_ras)
pu_val_index <- 1:ncell(base_ras)
```
#Feature dataframe
```{r}
# Load pre-processed matrices
load(file = "./inputs/spp_list_matrix.RData")
spp_df <- spp_list_mat
spp_df <- as.data.frame(spp_df)
# This function assigns weights to ensure that no species group dominates the optimisation
assign_taxon_weights <- function(groups){
	n <- length(unique(groups))
	animals <- c("amphibians", "birds", "mammals", "reptiles")
	plants <- unique(groups)[which(!unique(groups) %in% animals)]
	# number of animals
	na <- 4
	# number of plants
	np <- n - na
  # in the current case there are no birds, so just spreading the weights among the animal taxon
	wp <- 0 / np
	wa <- 1 / na
	w <- rep(0, length(groups))
	
	for (i in 1:length(animals)){
		w[which(groups == animals[i])] <- wa / length(which(groups == animals[i]))
	}

	for (i in 1:length(plants)){
		w[which(groups == plants[i])] <- wp / length(which(groups == plants[i]))
	}
	return(w)
}
spp_df$speciesweights <- assign_taxon_weights(groups=spp_df$taxon)

# species.pu.list --> which species occurs in which planning unit
load(file = "./inputs/species.pu.list.RData")

# Features dataframe --> analysis id number and IUCN id number
feat <- readRDS(file = "./inputs/feat.rds")

# Get the proportion of natural land
load(file = "./inputs/pu_df_matrix.RData")
propnat <- combined_matrix[,6]

# rij dataframe
# Create an empty sparse matrix
rowss <- nrow(feat)
colss <- length(pu_val)
iidx <- lapply(1:length(species.pu.list), function(i) rep(i, length(species.pu.list[[i]])))
spp_w <- lapply(1:length(species.pu.list), function(i) rep(spp_df[i,6], length(species.pu.list[[i]])))
spp_w <- unlist(spp_w)
iidx <- unlist(iidx)
jidx <- unlist(species.pu.list)

# Need to make the species values in the matrix proportional to the natural area
# Convert combined_matrix to a data.table
dt <- as.data.table(combined_matrix)
setkey(dt, puid)  # Set key for fast lookups
# Replace puid values in species.pu.list with corresponding propnat values
updated_species_pu_list <- lapply(seq_along(species.pu.list), function(i) {
  # Print the current progress
  cat("Processing list element:", i, "\n")
  # Get the current puid list and ensure it is numeric
  puids <- species.pu.list[[i]]
  # Perform the lookup
  result <- dt[J(as.numeric(puids)), on = "puid", propnat]
  # Replace NA values with 0
  result[is.na(result)] <- 0
  return(result)
})
natprop <- unlist(updated_species_pu_list)
vidx <- rep(1, length(jidx))

# Final species value
vidx <- vidx*spp_w*natprop

# Standardize carbon values
# Need to multiply cvals by the proportion of natural area
cvals <- combined_matrix[,3]*combined_matrix[,6]
# Standardise
cvals[terrestrial_index] = (cvals[terrestrial_index] - min(cvals[terrestrial_index])) / (max(cvals[terrestrial_index]) - min(cvals[terrestrial_index]))

# Check to see what the carbon values look like
# base_ras[1:ncell(base_ras)] = cvals
# plot(base_ras)

```
#Create weight matrix
```{r, echo = FALSE}
# Create weight matrix
weightm <- matrix(0, nrow=11, ncol=2)
nweights <- nrow(weightm)
# Populate the weight matrix with decreasing and increasing values
for (i in 1:nrow(weightm)) {
  weightm[i, ] <- c(1 - (i - 1) / 10, (i - 1) / 10)
}

weightm[1, 1] <- 1
weightm[1, 2] <- 0

weightm[2, 1] <- 0.999
weightm[2, 2] <- 0.001

weightm[3, 1] <- 0.998
weightm[3, 2] <- 0.002

weightm[4, 1] <- 0.997
weightm[4, 2] <- 0.003

weightm[5, 1] <- 0.9975
weightm[5, 2] <- 0.0025

weightm[6, 1] <- 0.996
weightm[6, 2] <- 0.004

weightm[7, 1] <- 0.995
weightm[7, 2] <- 0.005

weightm[8, 1] <- 0.99
weightm[8, 2] <- 0.01

weightm[9, 1] <- 0.98
weightm[9, 2] <- 0.02

weightm[10, 1] <- 0.95
weightm[10, 2] <- 0.05

weightm[11, 1] <- 0
weightm[11, 2] <- 1

# Print the weight matrix
print(weightm)
```
#Set target and locked in and out planning units
```{r}
# https://prioritizr.net/reference/add_locked_in_constraints.html
# Set target to 30% of terrestrial area
target <- length(terrestrial_index)*0.3
locked_in <- combined_matrix[,4]
locked_in <- locked_in[terrestrial_index]
locked_in <- as.logical(locked_in)

# Lock out the areas that are not available to protect
locked_out <- combined_matrix[,5]
locked_out <- locked_out[terrestrial_index]
locked_out <- as.logical(locked_out)
#Make sure that areas which are already protected stay protected
locked_out[locked_in] <- FALSE
sum(locked_out)

base_ras[terrestrial_index] <- locked_out
plot(base_ras)
```

# This is to run the analysis for different countries (30% for each country target) - maximum utility objective using prioritizr
```{r}
# Set up global parameters
locked_in <- combined_matrix[,4]
locked_in <- as.logical(locked_in)
locked_out <- combined_matrix[,5]
locked_out <- as.logical(locked_out)

sr_ras = raster("inputs/CBD-corrected_countries-code.tif")
base_ras = sr_ras - sr_ras

unique_values <- unique(sr_ras)
# Remove values that can't be run through the prioritisation for various reasons (eg. not enough planning units)

unique_values <- unique_values[!unique_values %in% c(28, 31, 47, 79, 136, 165, 186, 197)]
# unique_values <- unique_values[unique_values >= 29]

# Record countries that already have >30% protected
over_30_percent_protected_already <- c()

# Code to run the optimization for each country
for (m in unique_values){
print(m)
# Get indices for country of interest
indices <- which(values(sr_ras) == m, arr.ind = TRUE)
# Get locked in and out indices for country
locked_in_country <- locked_in[indices]
locked_out_country <- locked_out[indices]

# Skip and record if country already has >30% protected
if (sum(locked_in_country) > length(indices)*0.3) {
  print("PA estate is greater than 30% of country")
  over_30_percent_protected_already <- c(over_30_percent_protected_already, m)
} else {
  print("Less than 30% protected")
  target <- round(length(indices)*0.3)
  
# Combine the results into a data frame
df.results <- data.frame(matrix(nrow = nweights, ncol = 4))
colnames(df.results) <- c("biow", "cw", "bioval", "cval")

for (w in 1:nrow(weightm)) {
# Create global structures that are manipulated by weights
# Change feature values by the weight matrix - vidx*(weightm[w,1])
sparse_mat <- sparseMatrix(i = iidx, j = jidx, x = (vidx*(weightm[w,1])), dims = c(rowss-1, colss))
carbon_mat <- sparseMatrix(i = rep(1, length(cvals)), j = c(1:length(cvals)), x = cvals*weightm[w,2], dims = c(1, colss))

# Joint carbon values to species matrix
rij <- rbind(sparse_mat, carbon_mat)
  
pu_val <- rep(1, length(base_ras))
pu_val_index <- 1:ncell(base_ras)

# Restrict problem to just the country of interest
pu_val_country <- pu_val[indices]
rij_country <- rij[,indices]

# If else statement
if (sum(locked_out_country) > 0) {
  
  if (sum(locked_in_country) > 0) {
    p1 <-
    problem(pu_val_country, feat, rij_country) %>%
    add_max_utility_objective(target) %>%
    add_binary_decisions() %>%
    add_default_solver(gap = 0.005, verbose = FALSE, threads = num_cores) %>%
    add_locked_in_constraints(locked_in_country) %>%
    add_locked_out_constraints(locked_out_country)
  } else {
    p1 <-
    problem(pu_val_country, feat, rij_country) %>%
    add_max_utility_objective(target) %>%
    add_binary_decisions() %>%
    add_default_solver(gap = 0.005, verbose = FALSE, threads = num_cores) %>%
    add_locked_out_constraints(locked_out_country)
    }

} else {
  
  if (sum(locked_in_country) > 0) {
    p1 <-
    problem(pu_val_country, feat, rij_country) %>%
    add_max_utility_objective(target) %>%
    add_binary_decisions() %>%
    add_default_solver(gap = 0.005, verbose = FALSE, threads = num_cores) %>%
    add_locked_in_constraints(locked_in_country)
  } else {
    p1 <-
    problem(pu_val_country, feat, rij_country) %>%
    add_max_utility_objective(target) %>%
    add_binary_decisions() %>%
    add_default_solver(gap = 0.005, verbose = FALSE, threads = num_cores)
}
}

s1 <- solve(p1, force = TRUE)
save_index <- s1*indices

# Assuming 'save_index' is your vector
# Get a subset of values greater than 1 (ie. were selected)
selected <- save_index[save_index > 1]
saveRDS(selected, file = paste0(outfolderresults, "./", m, "_selected_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))
saveRDS(save_index, file = paste0(outfolderresults, "./", m, "_save_index_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))
}
write.csv(df.results, file = paste0(outfoldervals, "./", m, "_results_p0.csv"), row.names = TRUE)
}
}
```

#Plotting benefits for all countries
```{r}
country_numbers <- unique(sr_ras)
country_numbers <- country_numbers[!country_numbers %in% c(1, 4, 7, 28, 31, 47, 79, 136, 165, 186, 197)]

#4 just has 4 planning units
#No 15? 
#No 24?
#No 26?
#No 30? 
#No 36?
#No 46
#m <- 2

for (m in unique(country_numbers)){
  # Combine the results into a data frame
  df.results <- data.frame(matrix(nrow = nweights, ncol = 4))
  colnames(df.results) <- c("biow", "cw", "bioval", "cval")
  print(m)

  for (w in 1:nrow(weightm)) {
    #Get indices for country of interest
    indices <- which(values(sr_ras) == m, arr.ind = TRUE)

    if (file.exists(paste0(outfolderresults, "/", m, "_save_index_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))) {
      print("File exists!")
      # Load the RDS file
      save_index <- readRDS(paste0(outfolderresults, "/", m, "_save_index_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))
    
      # Initialize an empty vector for storing the proportions
      # prop_all <- numeric(length(species.pu.list))
      # sum_occ <- numeric(length(species.pu.list))
      # 
      # #Total sum of occurrences
      # for (i in 1:length(species.pu.list)) {
      #   # Count the number of elements in species.pu.list[[i]] that are also in newidx_set
      #   #common_elements <- sum(species.pu.list[[i]] %in% save_index)
      #   
      #   # Need to pull out the values proportional to the area that is "natural" land
      #   #spp_occ_vals_adjusted <- sparse_mat[i, save_index]
      # 
      #   sum_occ[i] <- sum(spp_occ_vals_adjusted)
      #   # Check if N is a multiple of 1,000,000
      #   if (i %% 10000 == 0) {
      #     print(i/length(species.pu.list) * 100)
      #   }
      # }
      # 
      # Extract values > 0
      values_greater_than_zero <- save_index[save_index > 0]
      spp_occ_vals_adjusted <- sparse_mat[, save_index]

      df.results[w, "biow"] <- weightm[w, 1]
      df.results[w, "cw"] <- weightm[w, 2]
      #df.results[w, "bioval"] <- mean(prop_all)
      #df.results[w, "bioval"] <- sum(sum_occ)
      df.results[w, "bioval"] <- sum(spp_occ_vals_adjusted)
      subset_cvals <- cvals[indices]
      df.results[w, "cval"] <- sum((subset_cvals)[which(save_index > 0)])
      
      #p = 0
      # Plot tradeoff curve
      #png(file = paste0(outfoldervals, "/countries/tradeoff_", "_", m, "_", p, ".png"), width = 1000, height = 1000)
      png(file = paste0(outfoldervals, "/countries/tradeoff_", m, ".png"), width = 1000, height = 1000)
      plot(df.results$bioval, df.results$cval, type = "b", pch = 16, lty = "solid",
           ylab = "Carbon sequestered",
           xlab = "Mean proportion of species range conserved")
      dev.off()
      
      # write.csv(df.results, file = paste0(outfoldervals, "/countries/", m, "_benefits_", weightm[w,1], "_wc_",  
      #weightm[w,2], "_p0.csv"), row.names = TRUE)
      
      write.csv(df.results, file = paste0(outfoldervals, "/countries/", m, "_benefits.csv"), row.names = TRUE)
 
      
  } else {
    print(paste0(m," File does not exist!"))
  }
  }
}

```



#Stitch together the selected planning units across all countries
```{r}
# Planning units ID layer
#sr_ras = raster("R:/RHODESFUT-Q3276/GBF-downscaling-analysis/Data/IIS_Rio_Data/CBD-corrected_countries-code.tif")
sr_ras = raster("C:/Data/Modelling_Beyer/z_GBF/Data/CBD-corrected_countries-code.tif")
base_ras = sr_ras - sr_ras
terrestrial_index = which(!is.na(base_ras[]))
base_ras[terrestrial_index] = 0
locked_in <- combined_matrix[,4]
locked_in <- as.logical(locked_in)

# Define the directory where your files are located
#directory <- "C:/Data/Modelling_Beyer/z_GBF/SEALS_GBF_preprocessing/outputs_v3/results_v3"
directory <- outfolderresults

for (i in 1:nrow(weightm)) {
selected <- c()
files_matching_pattern <- list.files(directory, pattern = paste0("save_index_ws_", weightm[i, 1], "_wc_", weightm[i, 2], "_p0.rds"))
# List files containing the specified pattern in the current directory
for (y in 1:length(files_matching_pattern)){
# Load the object from the RDS file
loaded_object <- readRDS(paste0("C:/Data/Modelling_Beyer/z_GBF/SEALS_GBF_preprocessing/outputs_v4/results_v4/", files_matching_pattern[y]))
selected <- c(selected, loaded_object)
}
# Get a list of all values that are greater than 0
values_greater_than_0 <- selected[selected > 0]
base_ras[values_greater_than_0] <- 1
base_ras[locked_in] <- 1

# Write the raster to a file
writeRaster(base_ras, filename = paste0("C:/Data/Modelling_Beyer/z_GBF/SEALS_GBF_preprocessing/", outfolderrasts, "/results_ws_", weightm[i, 1], "_wc_", weightm[i, 2], "_p0.tiff"), format = "GTiff", overwrite = TRUE)

saveRDS(selected, file = paste0(outfolderresults, "./save_index_global_ws_", weightm[i,1], "_wc_", weightm[i,2], "_p0.rds"))
}

```

#Plotting benefits for global priorities
```{r}
# Combine the results into a data frame
df.results <- data.frame(matrix(nrow = nweights, ncol = 4))
colnames(df.results) <- c("biow", "cw", "bioval", "cval")
sparse_mat <- sparseMatrix(i = iidx, j = jidx, x = (vidx*(weightm[w,1])), dims = c(rowss-1, colss))

for (w in 1:nrow(weightm)) {
#Get indices for country of interest
#indices <- which(values(sr_ras) == m, arr.ind = TRUE)

# Load the RDS file
save_index <- readRDS(paste0(outfolderresults, "./save_index_global_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))
#idx <- save_index[which(save_index > 0)]

# Initialize an empty vector for storing the proportions
# prop_all <- numeric(length(species.pu.list))
# sum_occ <- numeric(length(species.pu.list))

#Total sum of occurrences
# for (i in 1:length(species.pu.list)) {
#   # Count the number of elements in species.pu.list[[i]] that are also in newidx_set
#   common_elements <- sum(species.pu.list[[i]] %in% idx)
#   sum_occ[i] <- common_elements
#   # Check if N is a multiple of 1,000,000
#   if (i %% 1000 == 0) {
#     print(i/length(species.pu.list) * 100)
#   }
# }

values_greater_than_zero <- save_index[save_index > 0]
spp_occ_vals_adjusted <- sparse_mat[, save_index]

df.results[w, "biow"] <- weightm[w, 1]
df.results[w, "cw"] <- weightm[w, 2]
#df.results[w, "bioval"] <- mean(prop_all)
df.results[w, "bioval"] <- sum(spp_occ_vals_adjusted)
subset_cvals <- cvals[values_greater_than_zero]
df.results[w, "cval"] <- sum(subset_cvals)

}

p = 0
# Plot tradeoff curve
png(file = paste0(outfoldervals, "./tradeoff_pen_", "global_", p, ".png"), width = 1000, height = 1000)
plot(df.results$bioval, df.results$cval, type = "b", pch = 16, lty = "solid",
     ylab = "Carbon sequestered",
     xlab = "Mean proportion of species range conserved")
dev.off()

write.csv(df.results, file = paste0(outfoldervals, "./global.csv"), row.names = TRUE)


```

#MISC code
# This is to run the analysis globally (one 30% global target) - create problem with maximum utility objective and solve
```{r}
# Planning units ID layer
#sr_ras = raster("R:/RHODESFUT-Q3276/GBF-downscaling-analysis/Data/IIS_Rio_Data/CBD-corrected_countries-code.tif")
sr_ras = raster("C:/Data/Modelling_Beyer/z_GBF/Data/CBD-corrected_countries-code.tif")
base_ras = sr_ras - sr_ras
# Combine the results into a data frame
df.results <- data.frame(matrix(nrow = nweights, ncol = 4))
colnames(df.results) <- c("biow", "cw", "bioval", "cval")

w <- 1
#for (w in 1:nrow(weightm)) {
sparse_mat <- sparseMatrix(i = iidx, j = jidx, x = (vidx*(weightm[w,1]/dim(feat)[1])), dims = c(rowss-1, colss))
carbon_mat <- sparseMatrix(i = rep(1, length(cvals)), j = c(1:length(cvals)), x = cvals*weightm[w,2], dims = c(1, colss))
#Joint carbon values to species matrix
rij <- rbind(sparse_mat, carbon_mat)
#Restrict problem to just terrestrial units
pu_val <- pu_val[terrestrial_index]
rij <- rij[,terrestrial_index]

p1 <-
  problem(pu_val, feat, rij) %>%
  add_max_utility_objective(target) %>%
  add_binary_decisions() %>%
  add_default_solver(gap = 0.005, verbose = FALSE, threads = num_cores) %>%
  add_locked_in_constraints(locked_in) %>%
  add_locked_out_constraints(locked_out) 

#https://prioritizr.net/reference/add_neighbor_constraints.html
#p2 <- p1 %>% add_neighbor_constraints(1, data = adjacency_matrix(base_ras, directions = 8))

s1 <- solve(p1, force = TRUE)

saveRDS(s1, file = paste0(outfolder, "./results_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))
# Load an RDS file
s1 <- readRDS(paste0(outfolder, "/results_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))

# Plot the map
png(file=paste0(outfoldermaps, "./results_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0", ".png"), width=1000, height=1000)
base_ras[terrestrial_index] <- 1
base_ras[terrestrial_index] <- s1
# Display the raster with colors
plot(base_ras, col = c("gray", "dark green"), legend = FALSE)
# Add a legend
legend("topright", legend = c("Not Selected", "Selected"), fill = c("gray", "dark green"))
dev.off()

#Save the raster
writeRaster(base_ras, filename = paste0(outfolderrasts, "./results_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.tiff"), format = "GTiff", overwrite=TRUE)

#Export values
newidx <- terrestrial_index*s1
# Initialize an empty vector for storing the proportions
prop_all <- numeric(length(species.pu.list))
sum_occ <- numeric(length(species.pu.list))
# Create a set (unique values) from newidx for faster membership checks
newidx_set <- unique(newidx)

#Prop of species range conserved
# Loop through the species.pu.list
# for (i in 1:length(species.pu.list)) {
#   # Count the number of elements in species.pu.list[[i]] that are also in newidx_set
#   common_elements <- sum(species.pu.list[[i]] %in% newidx_set)
#   # Calculate the proportion
#   prop <- common_elements / length(species.pu.list[[i]])
#   # Store the proportion in the prop_all vector
#   prop_all[i] <- prop
#   # Check if N is a multiple of 1,000,000
#   if (i %% 1000 == 0) {
#     print(i/length(species.pu.list) * 100)
#   }
# }

#Total sum of occurances
for (i in 1:length(species.pu.list)) {
  # Count the number of elements in species.pu.list[[i]] that are also in newidx_set
  common_elements <- sum(species.pu.list[[i]] %in% newidx_set)
  sum_occ[i] <- common_elements
  # Check if N is a multiple of 1,000,000
  if (i %% 1000 == 0) {
    print(i/length(species.pu.list) * 100)
  }
}

df.results[w, "biow"] <- weightm[w, 1]
df.results[w, "cw"] <- weightm[w, 2]
#df.results[w, "bioval"] <- mean(prop_all)
df.results[w, "bioval"] <- sum(sum_occ)
df.results[w, "cval"] <- sum((cvals)[which(newidx > 0)])

write.csv(df.results, file = paste0(outfoldervals, "./results_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.csv"), row.names = TRUE)

rm(prop_all)
rm(newidx)

#}

```

```{r}
# Because of computational challenges we had to export that tables separately, so now we have to tie them together
# List all CSV files in the directory
csv_files <- list.files(path = "C:/Data/Modelling_Beyer/z_GBF/SEALS_GBF_preprocessing/outputs_v2/vals_v2", pattern = "*.csv", full.names = TRUE)

# Initialize an empty data frame to store the combined data
combined_data <- data.frame()

# Loop through each CSV file and combine the data
for (file in csv_files) {
  # Read the CSV file
  data <- read.csv(file, header = TRUE, sep = ",", na.strings = "NA")
  # Remove rows with NA values
  data <- data[complete.cases(data), ]
  # Append the data to the combined data frame
  combined_data <- rbind(combined_data, data)
}

# Sort the combined data frame in ascending order based on the 'X' column
combined_data <- combined_data[order(combined_data$biow), ]
df.results <- combined_data[1:11,]
p <- 0

# Plot tradeoff curve
png(file = paste0(outfoldervals, "./tradeoff_pen", p, ".png"), width = 1000, height = 1000)
plot(df.results$bioval, df.results$cval, type = "b", pch = 16, lty = "solid",
     ylab = "Mean proportion of species range conserved",
     xlab = "Carbon sequestered")
dev.off()

write.csv(df.results, file = paste0(outfoldervals, "./results_ws_all_weights_p0.csv"), row.names = TRUE)

```


#Plotting benefits for 1 country
```{r}

# Combine the results into a data frame
df.results <- data.frame(matrix(nrow = nweights, ncol = 4))
colnames(df.results) <- c("biow", "cw", "bioval", "cval")

m <- 3
w <- 1
for (w in 1:nrow(weightm)) {

#Get indices for country of interest
indices <- which(values(sr_ras) == m, arr.ind = TRUE)

# Load the RDS file
save_index <- readRDS(paste0(outfolderresults, "./", m, "_save_index_ws_", weightm[w,1], "_wc_", weightm[w,2], "_p0.rds"))

# Initialize an empty vector for storing the proportions
prop_all <- numeric(length(species.pu.list))
sum_occ <- numeric(length(species.pu.list))

#Total sum of occurrences
for (i in 1:length(species.pu.list)) {
  # Count the number of elements in species.pu.list[[i]] that are also in newidx_set
  common_elements <- sum(species.pu.list[[i]] %in% save_index)
  sum_occ[i] <- common_elements
  # Check if N is a multiple of 1,000,000
  if (i %% 1000 == 0) {
    print(i/length(species.pu.list) * 100)
  }
}

df.results[w, "biow"] <- weightm[w, 1]
df.results[w, "cw"] <- weightm[w, 2]
#df.results[w, "bioval"] <- mean(prop_all)
df.results[w, "bioval"] <- sum(sum_occ)
subset_cvals <- cvals[indices]
df.results[w, "cval"] <- sum((subset_cvals)[which(save_index > 0)])
}

p = 0
# Plot tradeoff curve
png(file = paste0(outfoldervals, "./tradeoff_pen_", "_", m, "_", p, ".png"), width = 1000, height = 1000)
plot(df.results$bioval, df.results$cval, type = "b", pch = 16, lty = "solid",
     ylab = "Carbon sequestered",
     xlab = "Mean proportion of species range conserved")
dev.off()

write.csv(df.results, file = paste0(outfoldervals, "./test.csv"), row.names = TRUE)


```

# Because of computational challenges we had to export that tables separately, so now we have to tie them together
```{r}
# List all CSV files in the directory
csv_files <- list.files(path = "C:/Data/Modelling_Beyer/z_GBF/SEALS_GBF_preprocessing/outputs_v3/vals_v3", pattern = "^16.*\\.csv$", full.names = TRUE)

# Initialize an empty data frame to store the combined data
combined_data <- data.frame()

# Loop through each CSV file and combine the data
for (file in csv_files) {
  # Read the CSV file
  data <- read.csv(file, header = TRUE, sep = ",", na.strings = "NA")
  # Remove rows with NA values
  data <- data[complete.cases(data), ]
  # Append the data to the combined data frame
  combined_data <- rbind(combined_data, data)
}

# Sort the combined data frame in ascending order based on the 'X' column
combined_data <- combined_data[order(combined_data$biow), ]
df.results <- combined_data[1:11,]
p <- 0

df.results <- read.csv("C:/Data/Modelling_Beyer/z_GBF/SEALS_GBF_preprocessing/outputs_v3/vals_v3/16_results_ws_0_wc_1_p0.csv")
# Plot tradeoff curve
png(file = paste0(outfoldervals, "./tradeoff_pen", p, ".png"), width = 1000, height = 1000)
plot(df.results$bioval, df.results$cval, type = "b", pch = 16, lty = "solid",
     ylab = "Mean proportion of species range conserved",
     xlab = "Carbon sequestered")
dev.off()

write.csv(df.results, file = paste0(outfoldervals, "./results_ws_all_weights_p0.csv"), row.names = TRUE)

```
